smdi: An R package to perform structural missing data investigations on partially observed confounders in real-world evidence studies

### 2023-12-05 manuscript/manuscript.qmd
last minute typo correction

```{r}
#| label: fig-examples
#| fig-cap: "Exemplary visual outputs of the a) smdi_vis(), b) gg_miss_upset(), c) smdi_asmd() and d) smdi_rf() functions, respectively. Sub-figure a) displays the proportion of missing observations for each partially observed covariate stratified by exposure. The upset plot in sub-figure b) demonstrates how a monotone missingness pattern between partially observed covariates can be visually inspected using a set visualization technique [@ruddle2022]. Sub-figure c) illustrates absolute standardized mean differences (ASMD) in patient characteristics between patients with and without a value observed for the PD-L1 (pdl1_num) biomarker as a measure of imbalance. Sub-figure d) demonstrates the variable importance of fully observed covariates for predicting missingness in the partially oberserved ECOG performance score variable (ecog_cat)."
#| echo: false
#| warning: false
#| fig-dpi: 400
#| fig-width: 22
#| fig-height: 11

>>>>

```{r}
#| label: fig-examples
#| fig-cap: "Exemplary visual outputs of the a) smdi_vis(), b) gg_miss_upset(), c) smdi_asmd() and d) smdi_rf() functions, respectively. Sub-figure a) displays the proportion of missing observations for each partially observed covariate stratified by exposure. The upset plot in sub-figure b) demonstrates how a monotone missingness pattern between partially observed covariates can be visually inspected using a set visualization technique [@ruddle2022]. Sub-figure c) illustrates absolute standardized mean differences (ASMD) in patient characteristics between patients with and without a value observed for the PD-L1 (pdl1_num) biomarker as a measure of imbalance. Sub-figure d) demonstrates the variable importance of fully observed covariates for predicting missingness in the partially observed ECOG performance score variable (ecog_cat)."
#| echo: false
#| warning: false
#| fig-dpi: 400
#| fig-width: 22
#| fig-height: 11
